---
title: "case_study_partI"
author: "Ananth Subramanian"
date: "February 18, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

The code below addresses the requirement of reading the files beer and breweries data and then merging them. The Brewery ID has been used as a Key while merging; In the eer data "Brewery_ID" has been renamed "Brew_ID" to match the brewery data. The resulting data is then transformed to a table to facilitate totalling and then reporting the highest IBU and ABV details based on the state

```{r case study}
getwd()
breweries_data <- read.csv(paste(getwd(),"Breweries.csv",sep ="/"))
View(breweries_data)
beer_data <- read.csv(paste(getwd(),"Beer.csv",sep ="/"))
View(beer_data)
beer_breweries_merge <- merge(breweries_data,beer_data, by = "Brew_ID")
View(beer_breweries_merge)
library(data.table)
beer_breweries_merged_table <- as.data.table(beer_breweries_merge)
```

## Including Plots



```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
